\cvsection{Grading Criteria}

\cvachievement{\faUniversity}{Attendance}{Attendance constitutes 5\% of the final grade for this course. Students may miss 3 classes without penalty. The overall attendance grade will fall one spot on the grade scale for each absence, starting with the fourth missed class period. Attendance will be taken during each class period. }

\divider

\cvachievement{\faLightbulbO}{Quizzes}{Students should expect to be assigned one quiz per week. They will be based on reading assignments, and other instructional material on Learn, and information introduced in lectures.}

\divider

\cvachievement{\faBarChart}{Datasets}{Linguistic analysis assignments based on sets of linguistic data will be assigned primarily during the first half of the course.}

\divider

\cvachievement{\faGroup}{Group Project}{Students will be assigned to groups to work together to create/deliver an oral presentation on a particular language, and complete exercises related to the language assigned to the group. Each language that will be assigned corresponds to a chapter in Part II of the required textbook.}

\divider

\cvachievement{\faKeyboardO}{Blogs}{Blogs provide an opportunity to discuss and compare information provided in the course with personal beliefs, observations, and experiences in an informal setting. There will be one prompt posted at the end of each week, based on the topic of that week. Your blog post should address the issues provided in the prompt. Students are required to comment on at least two other classmates' posts for the given week.} 
%Please remember to follow the expectations of courteous online discourse laid out in the Netiquette section of the syllabus. Students who fail to be respectful in their comments will lose points on the assignment. Informal writing is completely acceptable, as long as students are clear and appropriate in their posts.}

\divider

\cvachievement{\faFileTextO}{Final paper}{A linguistic autobiography is due on the day of the final exam as scheduled by UNM. This assignment provides the opportunity for you to reflect on your personal linguistic
background and general experiences with language, connecting your discussion with any of the topics
that have been addressed during this course.}